A deeper look into bug fixes: Patterns, replacements, deletions, and additions

### 2016-02-19 MSRChallenge2016.tex
through par approach

\vspace{1ex}
\noindent\textbf{How many files are changed to fix a bug?}
%
We consider a file changed if it is new, modified, or
deleted in a commit. In total, $52,052,571$ files were changed. Thus, on average each bug
fixing revision changes $11.3$ files.  This is surprisingly high:
most automatic program repair techniques assume that bugs are local.
We hypothesize several explanations. Other
software artifacts (e.g.  documentation) may be updated after bug  
fixing. It could also be the case that bug fixing commit also contains changes
that are not related to fixing bug (e.g. refactoring, adding new features by
creating new files). To better understand this
phenomenon, we ask:

@@

\begin{table}
\centering
  \begin{tabular}{ l | r  r }
  \toprule
  File Kind & Total & Average \\ 
  \midrule
  Binary & 752,945 & 0.16 \\ 
  Java (ERROR) & 2,073,558 & 0.45 \\ 
  Java (JLS2) & 2,607,413 & 0.57 \\ 
  Java (JLS3) & 15,748,967 & 3.43 \\
  Java (JLS4)  & 83,798 & 0.02 \\ 
  Text & 541,023 & 0.12 \\ 
  XML & 6,818,299 & 1.49 \\ 
  UNKNOWN & 23,426,568 & 5.10 \\ 
  \end{tabular}
  \caption{File Types of Changed Files}
  \label{tbl:fileType}
\end{table}

@@

\begin{table}
\centering
  \begin{tabular}{l | r  r }
  \toprule
  Introducing & Total Number & Average \\ \midrule
  Class & 729,201 & 0.16 \\ 
  Methods & 3,186,867 & 0.69 \\ 
  Fields & 6,076,646 & 1.32 \\ 
  Variables & 924,259 & 0.2 \\ 
  \end{tabular}
  \caption{Introducing new classes, methods, fields, local variables to fix bugs}
  \label{tbl:new}
\end{table}

@@

\section{PAR Bug Fixing Patterns}\label{sec:method}

Par is a well-known technique for patch generation that 
On the other hand, some approaches~\cite{kim2013} searches for specific patterns
and modifies java code according to predefined templates, constructed by humans
to cover a large set of bug fixes from an existing corpus.  As one of the only
techniques to directly target Java, it is an important source of possible
mutations to study to inform future directions. 
We therefore search for and analyze most of the bug fixing patterns proposed by
Kim et al.~\cite{kim2013} and assess their prevalence on this distinct
dataset by using Boa's language infrastructure~\cite{dyer2013} to identify the patterns
in the commits in the dataset.

@@

Boa's capabilities are powerful, but are limited in the precision it enables in
our detection of these patterns. For example, it is unable to directly perform a
diff between two file versions. Thus, rather than finding the exact count of
bug fixing patterns, we will find an approximate count by processing pre- and
post- fix files separately.  Additionally, there are
two of the originally proposed 10 patterns that cannot be easily detected by
Boa, as we describe below.

The patterns we search for are as follows, including our mechanism for
detecting them using Boa:

\vspace{1ex}
\noindent {\bf Altering method parameters (AMP)}.  This pattern changes the
input for method parameters.  {\bf Example:} obj.method(v1,v2) $\rightarrow$
obj.method(v1,v3). To detect this pattern, for both pre-fix and post-fix version
of a buggy file, we create a custom method call signature. This signature
contains method name, literal parameter, and variable parameter. we consider
parameter containing custom expression as OTHER. This is due to inexistence of
function that can print Abstract Syntax Tree (AST) back to source code in
Boa. We discard method signatures that appear both in pre-fix and post-fix
version. We then find whether there exists method with the same name and the
same number of parameters, but different parameter signatures in pre-fix and
post-fix version. If it exists, we consider that AMP pattern is found.

\vspace{1ex}
\noindent {\bf Calling another method with the same parameters (MSM)}.  This
pattern changes a method name.  {\bf Example:} obj.method1(param) $\rightarrow$
obj.method2(param).  To detect this pattern, we create method signature similar
like when detecting AMP pattern. This time, we find whether there exists method
with the exact same parameter signature but different name in pre-fix and
post-fix version. If it exists, we consider that MSM pattern is found.

\vspace{1ex}
\noindent
{\bf Calling another overloaded method with one more parameter (COM)}. This
pattern adds one more parameter to a method. 
	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2).
  To detect COM pattern, we create method signature similar like when detecting
  AMP and COM pattern. This time, we find whether there exists method with
  the same name, but the number of parameters in pre-fix and post-fix version
  differs by one. If it exists, we consider that COM pattern is found.

\vspace{1ex}
\noindent
 {\bf Changing a branch condition (CBC)}. This pattern adds or removes a condition.
	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0).
  To detect CBC pattern, we count the number of { \em logical and} and {\em
    logical or} inside if conditional expression for both pre-fix and post-fix
  version. we assume that the addition/removal of logical operators indicate
  addition/removal of condition. If there is a larger count in post-fix version, we consider that CBC pattern is found.

\vspace{1ex}
\noindent
 {\bf Initializing an object (IAO)}. This pattern adds a initialization to object declaration.
  To detect IAO pattern, we count the number of NEW expression in variable
  declaration for both pre-fix and post-fix version. If there is a larger count in post-fix version, we consider that IAO pattern
  is found.
	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type().

\vspace{1ex}
\noindent
 {\bf Adding a null checker (ANC)}.  This pattern inserts a condition to check whether an
    object is null or not in order to prevent unexpected state.
	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}
  To detect ANC pattern, we count the number of if conditional expression that
  contains {\em !=null} or {\em ==null} for both pre-fix and post-fix
  version. If there is a larger count in post-fix version,
  we consider that ANC pattern is found.

\vspace{1ex}
\noindent
 {\bf Adding an array out of bound checker (AOB)}. This pattern inserts a condition to check that an array
    index is within bound right before the index is used.
	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}.
  To detect AOB pattern, we count the number of if conditional expression that
  contains {\em expr<var.length} or {\em var.length>expr} for both pre-fix and
  post-fix version. If there is a larger count in post-fix version, we consider that AOB pattern is found.

\vspace{1ex}
\noindent
 {\bf Adding a collection out of bound checker (COB)}.  This pattern inserts a condition to check that a
    collection index is within bound before it is used.
	{\bf Example:} x=col.get(idx) $\rightarrow$ if(idx<col.size()){x=col.get(idx)}\\
To detect COB pattern, we count the number of if conditional expression that
contains {\em expr<col.size()} or {\em col.size()>expr} for both pre-fix and
post-fix version. If there are count differences between pre-fix and post-fix
version, we consider that COB pattern is found.

\vspace{1ex} The above patterns only cover 8 out of 10 bug fixing patterns in
PAR. The other two patterns are: (1) checking that an object is an instance of a
target class before casting it; and (2) replacing expression in an if condition
by another expression in the same scope. Pattern (1) cannot be analyzed because
Boa does not support {\em instanceof} expression. Similarly, pattern (2)
requires us to track scope between pre-fix and post-fix version, which is not
supported by Boa. Implementing them ourselves might be possible, but it might
require too much effort than necessary. We speculate that investigating 8 out of
10 patterns should give us a good idea on how common the patterns actually are.

>>>>

\vspace{1ex}
\noindent\textbf{How many files are changed to fix a bug?}
%
We consider a file changed if it is new, modified, or
deleted in a commit. In total, $52,052,571$ files were changed. Thus, on average each bug
fixing revision changes $11.3$ files.  This is surprisingly high:
most automatic program repair techniques assume that bugs are local.
We hypothesize several explanations. Other
software artifacts (e.g.  documentation) may be updated after bug  
fixing, or fixing commits may contain changes
unrelated to fixing bug (e.g. refactoring, adding new features by
creating new files). To better understand this
phenomenon, we ask:

@@

\begin{table}
\centering
  \begin{tabular}{ l | r  r }
  \toprule
  File Kind & Total & Average \\ 
  \midrule
  Binary & 752,945 & 0.16 \\ 
  Java (ERROR) & 2,073,558 & 0.45 \\ 
  Java (JLS2) & 2,607,413 & 0.57 \\ 
  Java (JLS3) & 15,748,967 & 3.43 \\
  Java (JLS4)  & 83,798 & 0.02 \\ 
  Text & 541,023 & 0.12 \\ 
  XML & 6,818,299 & 1.49 \\ 
  UNKNOWN & 23,426,568 & 5.10 \\ 
\bottomrule
  \end{tabular}
  \caption{File Types of Changed Files}
  \label{tbl:fileType}
\end{table}

@@

\begin{table}
\centering
  \begin{tabular}{l | r  r }
  \toprule
  Introducing & Total Number & Average \\ \midrule
  Class & 729,201 & 0.16 \\ 
  Methods & 3,186,867 & 0.69 \\ 
  Fields & 6,076,646 & 1.32 \\ 
  Variables & 924,259 & 0.2 \\ 
\bottomrule
  \end{tabular}
  \caption{Introducing new classes, methods, fields, local variables to fix bugs}
  \label{tbl:new}
\end{table}

@@

\section{Bug Fixing Patterns}\label{sec:method}

One of the best-known program repair techniques to target Java is
PAR~\cite{kim2013}.  Par searches for specific patterns
and modifies java code according to predefined templates, constructed by humans
to cover a large set of bug fixes from an existing corpus.  Par serves as an
important source of possible 
mutations to study to inform future directions. 
We therefore search for and analyze most of the bug fixing patterns proposed by
Kim et al. and estimate their prevalence in this
dataset.

@@

Boa's capabilities are powerful, butlimited in the precision it enables in
our detection of Par bug-fixing patterns. For example, it is unable to directly perform a
diff between two file versions. Thus, rather than finding the exact count of
bug fixing patterns, we find an approximate count by processing pre- and
post- fix files separately.  Additionally, there are
two of the originally proposed 10 patterns that cannot be easily detected by
Boa, as we describe below. 
%
The patterns we search for are as follows, including our mechanism for
detecting them using Boa:

\vspace{1ex}
\noindent {\bf Altering method parameters (AMP)}.  This pattern changes 
input method parameters. %(\texttt{obj.method(v1,v2) $\rightarrow$
%obj.method(v1,v3)}). 
To detect this pattern, for both pre-fix and post-fix version
of a buggy file, we create a custom method call signature that
contains the name, literal parameters, and variable parameters (more complex
expressions are listed as OTHER).
%  This is due to inexistence of
% function that can print Abstract Syntax Tree (AST) back to source code in
% Boa. 
We discard method signatures that appear both in pre-fix and post-fix
versions, and then identify methods with the same name and the
same number of parameters, but different parameter signatures in pre- and
post-fix versions.% If it exists, we consider that AMP pattern is found.

\vspace{1ex}
\noindent {\bf Calling another method with the same parameters (MSM)}.  This
pattern changes a method name. % (\texttt{obj.method1(param) $\rightarrow$
%obj.method2(param)}).  
To detect this pattern, we create method signature similar
to the above for the AMP pattern, looking for methods
with the exact same parameter signature but different names in pre- and
post-fix versions. %If it exists, we consider that MSM pattern is found.

\vspace{1ex}
\noindent
{\bf Calling another overloaded method with one more parameter (COM)}. This
pattern adds one more parameter to a method. %(\texttt{obj.method(v1) $\rightarrow$ obj.method(v1,v2)}).
We create method signature similar to the above, seeking methods with
  the same name, one more parameter in the post-fix version.

\vspace{1ex}
\noindent
 {\bf Changing a branch condition (CBC)}. This pattern adds or removes a condition.
%(e.g., \texttt{if(a != b) $\rightarrow$ if(a != b \&\& c == 0)}).
  To detect CBC pattern, we count the number of { \em logical and} and {\em
    logical or} inside if conditional expression sfor both pre-fix and post-fix
  version. We assume that the addition/removal of logical operators indicate
  addition/removal of condition. If there is a larger count in post-fix version,
  we consider the CBC pattern is found.

\vspace{1ex}
\noindent
{\bf Initializing an object (IAO)}. This pattern adds a initialization to object
declaration.  We count the number of NEW expressions in variable declarations
for both pre- and post-fix versions. If there is a larger count in post-fix
version, we consider that IAO pattern is found.

\vspace{1ex}
\noindent
 {\bf Adding a null checker (ANC)}.  This pattern inserts a condition to check whether an
    object is null.
%	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}
  To detect ANC pattern, we count the number of if conditional expressions that
  contains {\em !=null} or {\em ==null} for both pre-fix and post-fix
  version. If there is a larger count in post-fix version,
  we consider that ANC pattern found.

\vspace{1ex}
\noindent
 {\bf Adding an array out of bound checker (AOB)}. This pattern inserts a condition to check that an array
    index is within bound right before the index is used.
%	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}.
 We count the number of if conditional expression that
  contains {\em expr<var.length} or {\em var.length>expr} for both pre-fix and
  post-fix version. If there is a larger count in post-fix version, we consider that AOB pattern is found.

\vspace{1ex}
\noindent
 {\bf Adding a collection out of bound checker (COB)}.  This pattern inserts a condition to check that a
    collection index is within bound before it is used.
To detect COB pattern, we count the number of if conditional expression that
contains {\em expr<col.size()} or {\em col.size()>expr} for both pre-fix and
post-fix version. If there are count differences between pre-fix and post-fix
version, we consider the COB pattern found.

\vspace{1ex} The above patterns cover 8 out of 10 bug fixing patterns in
PAR. The other two patterns are (1) checking that an object is an instance of a
target class before casting it; and (2) replacing expression in an if condition
by another expression in the same scope. Pattern (1) cannot be analyzed because
Boa does not support the {\em instanceof} expression. Pattern (2)
requires us to track scope between pre-fix and post-fix version, which is not
easily supported by Boa.  Investigating 8 out of the
10 patterns should still provide a good idea on how common the patterns actually are.
